Guarded Recursion in Agda via Sized Types

### 2019-02-04 code-oneclock-paper/latex/paper.tex
Minor textual changes in abstract

\begin{abstract}
  In type theory, programming and reasoning with possibly
  non-terminating programs and potentially infinite objects is
  achieved using coinductive types. Recursively defined programs of
  these types are required to be productive to guarantee the
  consistency of the type system. Proof assistants such as Agda and
  Coq traditionally employ strict syntactic productivity checks, which
  commonly make programming with coinductive types convoluted.  One
  way to overcome this issue is by encoding productivity at the level
  of types, so that the type system forbids the implementation of
  non-productive corecursive programs.
%%, meaning
%%  that although their definitions can be unfolded \emph{ad infinitum},
%%  finite unfoldings are guaranteed to produce . 
  In this paper we compare two different approaches to type-based
  productivity: guarded recursion and sized types. More specifically,
  we show how to simulate guarded recursion in Agda using sized
  types. We formalize the syntax of a simple type theory for guarded
  recursion, corresponding to a variant of Atkey and McBride's
  calculus for productive coprogramming
  \cite{atkey2013productive}. Then we give a denotational semantics
  using presheaves over the preorder of sizes. Sized types are
  fundamentally employed in the interpretation of the characteristic
  features of guarded recursion, notably the fixpoint combinator.
%Sized types are fundamentally employed in the interpretation of the characteristic features of guarded recursion, notably the fixpoint combinator.
%%extending type theory with
%%  coinduction and coinductive types.  More specifically, we show that
%%  guarded recursion and guarded recursive types can be simulated with
%%  sized types.  We do this by defining a model of guarded recursion in
%%  type theory extended with sized types.  The model is variation of
%%  the topos of trees, and it is formalized in Agda.
\end{abstract}

>>>>

\begin{abstract}
  In type theory, programming and reasoning with possibly
  non-terminating programs and potentially infinite objects is
  achieved using coinductive types. Recursively defined programs of
  these types need to be productive to guarantee the
  consistency of the type system. Proof assistants such as Agda and
  Coq traditionally employ strict syntactic productivity checks, which
  commonly make programming with coinductive types convoluted.  One
  way to overcome this issue is by encoding productivity at the level
  of types, so that the type system forbids the implementation of
  non-productive corecursive programs.
%%, meaning
%%  that although their definitions can be unfolded \emph{ad infinitum},
%%  finite unfoldings are guaranteed to produce . 
  In this paper we compare two different approaches to type-based
  productivity: guarded recursion and sized types. More specifically,
  we show how to simulate guarded recursion in Agda using sized
  types. We formalize the syntax of a simple type theory for guarded
  recursion, which is a variant of Atkey and McBride's
  calculus for productive coprogramming
  \cite{atkey2013productive}. Then we give a denotational semantics
  using presheaves over the preorder of sizes. Sized types are
  fundamentally used to interpret the characteristic
  features of guarded recursion, notably the fixpoint combinator.
%Sized types are fundamentally employed in the interpretation of the characteristic features of guarded recursion, notably the fixpoint combinator.
%%extending type theory with
%%  coinduction and coinductive types.  More specifically, we show that
%%  guarded recursion and guarded recursive types can be simulated with
%%  sized types.  We do this by defining a model of guarded recursion in
%%  type theory extended with sized types.  The model is variation of
%%  the topos of trees, and it is formalized in Agda.
\end{abstract}
